\LARGE \bf Can a toluene-degrading bacteria improve the growth of a bacterial community in case of toluene pollution?

### 2017-12-14 Data_csv/Paper/paper.tex
s

\begin{figure}

	\begin{minipage}{.48\linewidth}
	%	\hspace{-0.3cm}
	%	\begin{subfigure}{.25\textwidth}
			\centering

			\includegraphics[width=1\linewidth]{t8_unstained_ppsc1.png}
			\captionof{figure}{Data of unstained sample (unstained PPSC, replicate 1, timepoint 8). Horizontal axis : intensity of red fluorescence. Vertical axis : intensity of green fluorescence.}
			\label{scatter1}

	%	\end{subfigure}%
	%	\begin{subfigure}{.22\textwidth}
	\end{minipage}\hspace{.2cm}
	\begin{minipage}{.48\linewidth}

			\centering

			\includegraphics[width=1\linewidth]{t8_stained_ppsc1.png}
			\captionof{figure}{Data of stained sample (stained PPSC, replicate 1, timepoint 8). Horizontal axis : intensity of red fluorescence. Vertical axis : intensity of green fluorescence.}
			\label{scatter2}

	%	\end{subfigure}
	%	\caption{Fig. \ref{scatter1}: Data of unstained sample (unstained PPSC, replicate 1, timepoint 8). Fig. \ref{scatter2}: Data of stained sample (stained PPSC, replicate 1, timepoint 8). Horizontal axis : intensity of red fluorescence. Vertical axis : intensity of green fluorescence.}
	%	\label{scatterplot}
	\end{minipage}

@@

\subsubsection{Sand Community}
The growth of the sand community in each treatment for the first week is represented in Fig. \ref{SCgrowth1}.
There is an important interaction between the explicative variables (F = 26.62, df = 1, $p = 8.64\cdot 10 ^{-4}$).
In mixed carbon, SC grows similarly in presence or absence of PP (black and blue curve).
In toluene however, the presence of PP allows for a 1000-fold difference on average (red and yellow curves).
We conclude that the presence of PP affects SC differently depending on the media. In toluene, it allows for a better growth but has no effect in the mix carbon media. In addition, the effect of the media on SC is important in absence of PP. SC alone grows less in toluene than in mixed carbon.\newline
%There is an important difference between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$). It is clearly shown on the Fig. \ref{PPgrowth1} (red and yellow curves vs black and blue curves).
%In contrast, our data shows no significant difference due to the presence or absence of the sand community and no interaction.
%We conclude that SC has no effect on the growth of PP and that PP grows better in toluene only than in mixed carbon. It is certainly due the greater amount of carbon in the toluene media.
\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{AUCsc1.png}
	\caption{Week 1 - SC : AUC (Area Under the Curve). Each point represents the data from each well of the plate.}
	\label{aucscw1}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{AUCpp1.png}
	\caption{Week 2 - PP : AUC (Area Under the Curve). Each point represents the data from each well of the plate.}
	\label{aucppw1}
\end{figure}

\subsubsection{Pseudomonas putida}
There is an important difference between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$). It is clearly shown on the Fig. \ref{PPgrowth1} (red and yellow curves vs black and blue curves).
In contrast, our data shows no significant difference due to the presence or absence of the sand community and no interaction.
We conclude that SC has no effect on the growth of PP and that PP grows better in the Toluene medium than in the mix carbon medium. It could be due to the greater amount of carbon in the toluene media.

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{totcount_mixC2.PNG}
	\caption{Total count (SYTO-9 Count + mCherry count) of SC, PV and PVSC over time in a mixed carbon medium during the second week.}
	\label{totcountmixC2text}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{totcount_tol2.PNG}
	\caption{Total count (SYTO-9 count + mCherry count) of SC, PV and PVSC over time in a toluene only medium during the second week.}
	\label{totcounttol2text}
\end{figure}
\subsubsection{Sand Community}
The growth of the sand community in each treatment for the second week is represented in Fig. \ref{SCgrowth2}.
In contrast with the first week, SC was able to grow in toluene. It is not surprising, as a community extracted from sand is typically composed of many kinds of bacteria. It is likely that at least one of them can degrade a given carbon source. But it shows that the sand community we extracted behaved differently from one week to another and thus cannot be considered similar. Therefore, we won't be able to compare the results from the two weeks. 
The anova on the area under the curve shows no significant effect of any explicative variables, but we believe the results could be different if we continued the culture for a day because we can see on the growth graph that SC alone is still in exponential growth at 48 hours in toluene. It is plausible that with a few more timepoints, SC would grow better alone than in presence of PV.\newline

\subsubsection{Pseudomonas veronii}
The growth of the PV in each treatment is represented in Fig. \ref{PVgrowth2}.
As in the first week, there is an important difference of growth between the media (F = 784.71, df = 1, $p = 2.85 \cdot 10^{-9}$). PP grew about a hundred-fold greater in toluene (red and orange) than in mixed carbon (black and blue curves).
One can also notice that PP grew slightly less in presence of SC, in both media (blue and yellow compared to black and red curves). The difference in area under the curve is significant (F = 5.56, df = 1, $p = 0.046$).While not being as significant as our other results, it seems to indicate some competition between them in this type of culture. It seems plausible, knowing from previous experiments that PV grows a bit slower than PP and in this experiment some bacteria from the sand community were able to grow on toluene.
\newline

\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{AUCsc2.png}
	\caption{Week 2 - SC : AUC (Area Under the Curve). Each point represents the data from each well of the plate.}
	\label{aucscw2}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{AUCpv2.png}
	\caption{Week 2 - PV : AUC (Area Under the Curve). Each point represents the data from each well of the plate.}
	\label{aucpvw2}
\end{figure}

@@

In our experiments, PP and PV were able to grow in both media in presence or absence of SC. This led us to think that PP and PV would be interesting candidates for bioaugmentation, especially as they have no problem growing with SC in mixed carbon. In addition, it seems that PP has a good growth in presence of SC, while PV has low growth in presence of SC. It makes PP a better candidate than PV for bioaugmentation.
Further experiments would be required to know if this is also true in a sand medium and especially over a longer period of time. Similar experiments could also be performed on different native communities. Also, it would be interesting to vary the concentration of toluene in these experiments.

@@

\begin{figure}

		\centering
		\includegraphics[width=9cm]{problemw1.PNG}
		\caption{Total count of green stained cells in toluene for PP alone and PP with SC during week 1. It showed no significant differences.}
		\label{problemw1}
\end{figure}

@@

>>>>

\begin{figure}
		\hspace{-0.3cm}
		\begin{subfigure}{.25\textwidth}
			\centering			
			\includegraphics[width=4.3cm]{t8_unstained_ppsc1.png}
			\caption{}
			\label{scatter1}			
		\end{subfigure}%
		\begin{subfigure}{.22\textwidth}		
			\centering			
			\includegraphics[width=4.3cm]{t8_stained_ppsc1.png}
			\caption{}
			\label{scatter2}			
		\end{subfigure}
		\caption*{Fig. \ref{scatter1}: Data of unstained sample (unstained PPSC, replicate 1, timepoint 8). \\ Fig. \ref{scatter2}: Data of stained sample (stained PPSC, replicate 1, timepoint 8). Horizontal axis : intensity of red fluorescence. Vertical axis : intensity of green fluorescence.}
		\label{scatterplot}
		\vspace{-0.5cm}
\end{figure}

@@

\subsubsection{Sand Community}
The growth of the sand community in each treatment for the first week is represented in Fig. \ref{aucscw1} and \ref{SCgrowth1}.
There is an important interaction between the explicative variables (F = 26.62, df = 1, $p = 8.64\cdot 10 ^{-4}$).
In mixed carbon, SC grows similarly in presence or absence of PP (black and blue points).
In toluene however, the presence of PP allows for a 1000-fold difference on average (red and yellow points).
We conclude that the presence of PP affects SC differently depending on the media. In toluene, it allows for a better growth but has no effect in the mix carbon media. In addition, the effect of the media on SC is important in
\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{AUCsc1.png}
	\caption{Week 1 - SC : Each point represents one of the three replicates's AUC for each treatment.}
	\label{aucscw1}
\end{figure}%
\vspace{-0.4cm}
\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{AUCpp1.png}
	\caption{Week 1 - PP : Each point represents one of the three replicates's AUC for each treatment.}
	\label{aucppw1}
\end{figure}
absence of PP. SC alone grows less in toluene than in mixed carbon.\newline
%There is an important difference between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$). It is clearly shown on the Fig. \ref{PPgrowth1} (red and yellow curves vs black and blue curves).
%In contrast, our data shows no significant difference due to the presence or absence of the sand community and no interaction.
%We conclude that SC has no effect on the growth of PP and that PP grows better in toluene only than in mixed carbon. It is certainly due the greater amount of carbon in the toluene media.

\subsubsection{Pseudomonas putida}
There is an important difference between the media (F =907.30, df = 1, $p = 2.36 \cdot 10^{-6}$). It is clearly shown on the Fig. \ref{aucppw1} and \ref{PPgrowth1} (red and yellow curves/points vs black and blue curves/points)).
In contrast, our data shows no significant difference due to the presence or absence of the sand community and no interaction.
We conclude that SC has no effect on the growth of PP and that PP grows better in the Toluene medium than in the mix carbon medium. It could be due to the greater amount of carbon in the toluene media.

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{totcount_mixC2.PNG}
	\caption{Total count (SYTO-9 Count + mCherry count) of SC, PV and PVSC over time in a mixed carbon medium during the second week.}
	\label{totcountmixC2text}
\end{figure}
\vspace{-0.4cm}
\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{totcount_tol2.PNG}
	\caption{Total count (SYTO-9 count + mCherry count) of SC, PV and PVSC over time in a toluene only medium during the second week.}
	\label{totcounttol2text}
\end{figure}
\subsubsection{Sand Community}
The growth of the sand community in each treatment for the second week is represented in Fig. \ref{aucscw2} and \ref{SCgrowth2}.
In contrast with the first week, SC was able to grow in toluene (red curves/points). It is not surprising, as a community extracted from sand is typically composed of many kinds of bacteria. It is likely that at least one of them can degrade a given carbon source. But it shows that the sand community we extracted behaved differently from one week to another and thus cannot be considered similar. Therefore, we won't be able to compare the results from the two weeks. 
The anova on the area under the curve shows no significant effect of any explicative variables, but we believe the results could be different if we continued the culture for a day because we can see on the growth graph that SC alone is still in exponential growth at 48 hours in toluene. It is plausible that with a few more timepoints, SC would grow better alone than in presence of PV.\newline

\subsubsection{Pseudomonas veronii}
The growth of the PV in each treatment is represented in Fig. \ref{aucpvw2} and \ref{PVgrowth2}.
As in the first week, there is an important difference of growth between the media (F = 784.71, df = 1, $p = 2.85 \cdot 10^{-9}$). PP grew about a hundred-fold greater in toluene (red and orange) than in mixed carbon (black and blue curves/points).
One can also notice that PP grew slightly less in presence of SC, in both media (blue and yellow compared to black and red curves/points). The difference in area under the curve is significant (F = 5.56, df = 1, $p = 0.046$).While not being as significant as our other results, it seems to indicate some competition between them in this type of culture. It seems plausible, knowing from previous experiments that PV grows a bit slower than PP and in this experiment some bacteria from the sand community were able to grow on toluene.
\newline

\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{AUCsc2.png}
	\caption{Week 2 - SC : Each point represents one of the three replicates's AUC for each treatment.}
	\label{aucscw2}
\end{figure}%
\vspace{-0.3cm}
\begin{figure}[H]
	\centering
	\includegraphics[width=9cm]{AUCpv2.png}
	\caption{Week 2 - PV : Each point represents one of the three replicates's AUC for each treatment.}
	\label{aucpvw2}
\end{figure}

@@

In our experiments, PP and PV were able to grow in both media in presence or absence of SC. This led us to think that PP and PV would be interesting candidates for bioaugmentation, especially as they have no problem growing with SC in mixed carbon.

As PV showed a significantly lower growth on average in toluene in presence of SC than PP, it would be tempting to say that PP would be an even better candidate. However, as said in results section B2, our data isn't totally reliable to compare the two strains, as the SC extracted the two weeks behaved differently. It would be good to test the PP and PV on the same SC.

Further experiments would be required to know if this is also true in a sand medium (and not liquid medium) and especially over a longer period of time. Similar experiments could also be performed on different native communities. Also, it would be interesting to vary the concentration of toluene in these experiments.

@@

\begin{figure}
		\centering
		\includegraphics[width=9cm]{problemw1.PNG}
		\caption{Total count of green stained cells in toluene for PP alone and PP with SC during week 1. It showed no significant differences.}
		\label{problemw1}
\end{figure}

@@

%$\displaystyle\frac{\text{nbr of colonies } \cdot \text{ dilution factor } \cdot \text{ 100 $\mu$L of 1mL total}}{\text{estimated orginal number of cells}} = $\\
%
%
%$\displaystyle\frac{1109 \cdot 25 \cdot 10}{2\cdot 10^{9}}= 1.39 \cdot 10 ^{-4}$
